Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-10-07 paper_comparison/paper_comparison/paper_comparison.Rmd
solve c-interesting

```{=tex}
\begin{equation} \label{eq:pvalue-beta-binomial}
P(C \geq c_i) = \sum_{x=c_i}^{K}\frac{\Gamma(K + 1)}{\Gamma(x + 1)\Gamma(K - x + 1)}\frac{B(x + \alpha, K - x + (m - 1)\alpha)}{B(\alpha, (m-1)\alpha)},
\end{equation}
```

@@

and $\Gamma(.)$ is the gamma function defined as

```{=tex}
\begin{equation} \label{eq:gammafunction}
\Gamma(z) = \int_{0}^{\infty}t^{z - 1}e^{-t}dt,\quad \text{where}\quad z>0. 
\end{equation}
```

@@

The parameter $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} is usually unknown and hence needs to be estimated from the survey data. For low values of $\alpha$, only a few plots are attractive to the observers and tend to be selected. For higher values of $\alpha$, the distribution of the probability of each plot being selected is more evenly. @vanderplas2021statistical suggested that $\alpha$ can be estimated using maximum likelihood estimation or visual estimation. But if $\alpha$ is small and only a few null plots in a lineup are attractive, MLE could fail to provide accurate estimates.

@@

Instead, we directly estimated the probability of a lineup being rejected using a logistic regression with the natural logarithm of the effect size as the only regressor formulated as:

@@

Effect $E$ is derived from the Kullback-Leibler divergence (see [appendix ref here]) formulated as:

>>>>

```{=tex}
\begin{equation} \label{eq:pvalue-beta-binomial}
P(C \geq c_i) = \sum_{x=c_i}^{K}{K \choose x}\frac{B(x + \alpha, K - x + (m - 1)\alpha)}{B(\alpha, (m-1)\alpha)},
\end{equation}
```

@@

Note that Equation \ref{eq:pvalue-beta-binomial} only works with integer $c_i$. For non-integer $c_i$, linear approximation will be applied to calculate the p-value

```{=tex}
\begin{equation} \label{eq:pvalue-beta-binomial-approx}
P(C \geq c_i) = P(C \geq \lceil c_i \rceil) + (\lceil c_i \rceil - c_i) P(C = \lfloor c_i \rfloor), \quad \text{for}\quad c_i \notin \mathbb{Z}.
\end{equation}
```

@@

Besides, the parameter $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} is usually unknown and hence needs to be estimated from the survey data. For low values of $\alpha$, only a few plots are attractive to the observers and tend to be selected. For higher values of $\alpha$, the distribution of the probability of each plot being selected is more evenly. @vanderplas2021statistical defined that a plot is $c$-interesting if $c$ or more participants selected the plot as the most different. Given the definition, The expected number of plots selected at least $c$ times, $E[Z_c]$, is calculated as

```{=tex}
\begin{equation} \label{eq:c-interesting-expectation}
E[Z_c(\alpha)] = \frac{m}{B(\alpha, (m-1)\alpha)}\sum_{\lceil c \rceil}^{K}{K \choose x} B(x + \alpha, K - x + (m-1)\alpha).\end{equation}
```

@vanderplas2021statistical suggested that $\alpha$ can be estimated using MLE and Equation \ref{eq:c-interesting-expectation}. But for precise estimate of $\alpha$, additional responses to Rorschach lineups, which is a type of lineup consists of only null plots, are required.

<!-- But if $\alpha$ is small and only a few null plots in a lineup are attractive, MLE could fail to provide accurate estimates. -->

@@

Instead, we directly estimated the probability of a lineup being rejected using a logistic regression with the natural logarithm of the effect size as the only regressor formulated as

@@

Effect $E$ is derived from the Kullback-Leibler divergence (see [appendix ref here]) formulated as

### 2022-10-07 paper_comparison/paper_comparison/paper_comparison.tex
fix the p-value calc
solve c-interesting

\begin{equation} \label{eq:pvalue-beta-binomial}
P(C \geq c_i) = \sum_{x=c_i}^{K}\frac{\Gamma(K + 1)}{\Gamma(x + 1)\Gamma(K - x + 1)}\frac{B(x + \alpha, K - x + (m - 1)\alpha)}{B(\alpha, (m-1)\alpha)},
\end{equation}

@@

and \(\Gamma(.)\) is the gamma function defined as

\begin{equation} \label{eq:gammafunction}
\Gamma(z) = \int_{0}^{\infty}t^{z - 1}e^{-t}dt,\quad \text{where}\quad z>0. 
\end{equation}

The parameter \(\alpha\) used in Equation \ref{eq:pvalue-beta-binomial}
is usually unknown and hence needs to be estimated from the survey data.
For low values of \(\alpha\), only a few plots are attractive to the
observers and tend to be selected. For higher values of \(\alpha\), the
distribution of the probability of each plot being selected is more
evenly. \citet{vanderplas2021statistical} suggested that \(\alpha\) can
be estimated using maximum likelihood estimation or visual estimation.
But if \(\alpha\) is small and only a few null plots in a lineup are
attractive, MLE could fail to provide accurate estimates.

@@

Effect \(E\) is derived from the Kullback-Leibler divergence (see
{[}appendix ref here{]}) formulated as:

@@

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-7-1} \end{center}

>>>>

\begin{equation} \label{eq:pvalue-beta-binomial}
P(C \geq c_i) = \sum_{x=c_i}^{K}{K \choose x}\frac{B(x + \alpha, K - x + (m - 1)\alpha)}{B(\alpha, (m-1)\alpha)},
\end{equation}

@@

Note that Equation \ref{eq:pvalue-beta-binomial} only works with integer
\(c_i\). For non-integer \(c_i\), linear approximation will be applied
to calculate the p-value

\begin{equation} \label{eq:pvalue-beta-binomial-approx}
P(C \geq c_i) = P(C \geq \lceil c_i \rceil) + (\lceil c_i \rceil - c_i) P(C = \lfloor c_i \rfloor), \quad \text{for}\quad c_i \notin \mathbb{Z}.
\end{equation}

Besides, the parameter \(\alpha\) used in Equation
\ref{eq:pvalue-beta-binomial} is usually unknown and hence needs to be
estimated from the survey data. For low values of \(\alpha\), only a few
plots are attractive to the observers and tend to be selected. For
higher values of \(\alpha\), the distribution of the probability of each
plot being selected is more evenly. \citet{vanderplas2021statistical}
defined that a plot is \(c\)-interesting if \(c\) or more participants
selected the plot as the most different. Given the definition, The
expected number of plots selected at least \(c\) times, \(E[Z_c]\), is
calculated as

\begin{equation} \label{eq:c-interesting-expectation}
E[Z_c(\alpha)] = \frac{m}{B(\alpha, (m-1)\alpha)}\sum_{\lceil c \rceil}^{K}{K \choose x} B(x + \alpha, K - x + (m-1)\alpha).\end{equation}

\citet{vanderplas2021statistical} suggested that \(\alpha\) can be
estimated using MLE and Equation \ref{eq:c-interesting-expectation}. But
for precise estimate of \(\alpha\), additional responses to Rorschach
lineups, which is a type of lineup consists of only null plots, are
required.

@@

Effect \(E\) is derived from the Kullback-Leibler divergence (see
{[}appendix ref here{]}) formulated as

@@

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-6-1} \end{center}
